Check links on old pages

### 2024-06-25 src/audit-old-pages.Rmd
Added audit-cross-links

---
title: "Check links on old pages"
author: "Steve Simon"
date: "Created 2023-02-20"
output: html_document
---

@@

```{r setup}
suppressMessages(suppressWarnings(library(glue)))
suppressMessages(suppressWarnings(library(magrittr)))
suppressMessages(suppressWarnings(library(readr)))
suppressMessages(suppressWarnings(library(stringr)))

# pad single digits with leading zero
zpad <- function(x) {
  ifelse(nchar(x)==1, paste0("0", x), x)
}
```

```{r find-files}
sub_dir_list <- c("99", zpad(0:12), "12a", zpad(13:18))

path1 <- "c:/Users"
path2 <- "dropbox/professional/fun stuff/update-website"

list.files(path1) %>%
  str_subset("(Simons)|(steve)") -> me

path3 <- glue("{path1}/{me}/{path2}")

print(glue("Searching in {path3}"))

list.files(path3)
```

```{r search-files}
key_text <- "<p>This page"
n_files <- 0
n_unlinked <- 0
for (sub_dir in sub_dir_list) {
  # List all html files in a specific folder
  full_path <- glue("{path3}/{sub_dir}/") 
  full_path %>%
    list.files %>%
    str_subset("html$") -> html_list
  i_files <- length(html_list)
  i_unlinked <- 0
  for (fn in html_list) {
    # Read text from html files
    file_text <- read_lines(glue("{full_path}/{fn}"))
    # Search for key phrase
    key_line <- str_subset(file_text, key_text)
    if (length(key_line) > 0) {next}
    # List files without key phrase
    i_unlinked <- i_unlinked + 1
    print(glue("{sub_dir}/{fn} has no link to new page"))
  }
  cat("\n")
  print(glue("{sub_dir} has {i_files} files. {i_unlinked} are unlinked."))
  cat("\n")
  n_files <- n_files + i_files
  n_unlinked <- n_unlinked + i_unlinked
}
print(glue("All directories have a total of  {n_files} files. {n_unlinked} are unlinked."))
```

>>>>

---
title: "Check links on old pages"
author: "Steve Simon"
date: "Created 2024-06-25"
output: html_document
---

@@

```{r setup}
suppressMessages(suppressWarnings(library(glue)))
suppressMessages(suppressWarnings(library(magrittr)))
suppressMessages(suppressWarnings(library(readr)))
suppressMessages(suppressWarnings(library(stringr)))
suppressMessages(suppressWarnings(library(tidyverse)))

path1 <- "c:/Users"
path2 <- str_subset(list.files(path1), "steve|simons")
path3 <- "Dropbox/professional/fun stuff/update-website"

"c:/Users/steve/Dropbox/professional/fun stuff/update-website"
"c:/Users/simons/Dropbox/professional/fun stuff/update-website"

html_path <- paste(path1, path2, path3, sep="/")
subdir_list=c(
  "00",
  "00files",
  "01",
  "02",
  "03",
  "04",
  "05",
  "06",
  "07",
  "08",
  "08a",
  "09",
  "10",
  "11",
  "12",
  "12a",
  "13",
  "14",
  "15",
  "16",
  "17",
  "18",
  "99",
  "archive",
  "category",
  "definitions",
  "weblog",
  "08/accrual",
  "08/definitions",
  "08/diagnostic",
  "08/faq",
  "08/images",
  "08/journal",
  "08/koans",
  "08/software",
  "08/training",
  "08/training/abstracts",
  "08/training/datasets",
  "08/training/exercises",
  "08/training/extras",
  "08/training/images",
  "08/website")
save_file <- "../data/check_old.RData"
```

### create html

```{r create}
html <- NULL
for (yr in rev(subdir_list)) {
  file_path <- paste(html_path, yr, sep="/")
  file_path %>%
    list.files(pattern="asp|htm$|html$") -> piper
  if (length(piper) == 0) next
  piper %>%
    str_remove("\\..*") -> fn
  piper %>%
    str_remove(".*\\.") -> ext
  data.frame(yr=yr, fn=fn, ext=ext) %>%
    bind_rows(html) -> html
}
n <- nrow(html)
```

### Search for links to old files

```{r links}
search_link <- function(tx) {
  prefix1 <- '<p>This page is moving to a <a href="'
  prefix2 <- '<p>This page has moved to a <a href="'
  postfix <- '">new website</a>.</p>'
  prepost <- paste(prefix1, prefix2, postfix, sep="|")
  website <- "http://new.pmean.com/"
  slash   <- "/"
  tx %>%
    str_subset(prepost) %>%
    str_replace(prefix1, "") %>%
    str_replace(prefix2, "") %>%
    str_replace(postfix, "") %>%
    str_replace(website, "") %>%
    str_replace(slash,   "") %>%
    paste0("") -> piper
  piper %>%
    paste0(collapse=", ")
}
```

### Search for size

```{r size}
search_size <- function(tx) {
  ty <- str_remove_all(tx, "\\s")
  length(tx)-sum(ty == "")
}
```

### Read file text

```{r read}
full_name <-
  paste0(
  html_path, "/",
  html$yr, "/",
  html$fn, ".",
  html$ext)
html$size <- -1
html$link <- "999"
for (i in 1:n) {
  tx <- read_lines(full_name[i])
  html$link[i] <- search_link(tx)
  html$size[i] <- search_size(tx)
}
html$miss <- as.numeric(nchar(html$link) == 0)
html$stub <- as.numeric(html$size <= 10)
save(html, file=save_file)
```

### Simple statistics

```{r simple}
summary(html$size)
count(html, ext)
count(html, miss)
count(html, stub)
```
